---
title: "Prediction Assignment"
author: "Pavel Bukhtik"
date: "18/06/2017"
output:
  md_document: default
---

## Overview

One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, my goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants and predict the manner in which they did the exercise.

More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

## Loading Data

Let’s begin with loading the training and testing datasets and performing a quick overview of the data we have.

Loading the data can request some time.

```{r cache=TRUE}
trainDataURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testDataURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
temp <- tempfile() 
download.file(trainDataURL, temp)
training <- read.csv(temp, stringsAsFactors = FALSE)
unlink(temp)
temp <- tempfile() 
download.file(testDataURL, temp)
testing <- read.csv(temp, stringsAsFactors = FALSE)
unlink(temp)

dim(training)
```

As you see above, training dataset contains 160 variables and 19622 observations. Thus you can find the information about the variables on the official site (http://groupware.les.inf.puc-rio.br/har)

## Pre-processing Data

There are many NA values in the data set, so we use KnnImpute method to impute those values. Besides, we try to standardize each features and use PCA to reduce features.

```{r}
library(caret)
library(RANN)
set.seed(12)
training$classe <- as.factor(training$classe)
training <- training[,-nearZeroVar(training)]
training <- training[,-c(1,2,3,4,5,6,7)]
inTrain <- createDataPartition(y=training$classe, p=0.75, list=FALSE)
training <- training[inTrain,]
validation <- training[-inTrain,]
preProc <- preProcess(training[,-length(training)],method=c("center", "scale", "knnImpute", "pca"), thresh=0.9)
cleanData <- predict(preProc,training)
```

Now data is ready for building a model.

## Building model

After getting the clean data set from the above processing, we use "knn" method to build the model. We use testing data to evaluate the performance of our model. It will take a time to fit our model.

```{r cache=TRUE}
fit <- train(classe ~., data=cleanData, method="knn")
```

Now we can check the accuracy of our model on the validation data.

```{r}
test <- predict(preProc, validation[,-length(validation)])
confusionMatrix(validation$classe, predict(fit,test))
```

As you can see we have reached accuracy of 0.9761. It is a good result.

## Prediction

After fitting the model, we can predict data for the test data. The result you can see below.

```{r cache=TRUE}
testing <- testing[,names(testing) %in% names(training)]
test <- predict(preProc, testing)
predict_result <- predict(fit, test)
predict_result
```

## Conclusion

* We can predict new data with the model we build.
* Accuracy of our model is 0.9761.
